A thesis draft

### 2018-11-16 res/sections/25-Tests.tex
Spellcheck and 80 columns

It is worth saying that Docker metrics are generally more precise than the
Virtual Box one: Docker allows to inspect the container and to gain startup and
shutdown times with a precision of millseconds, while to gather this information
for VirtualBox instances we had to use the command line utility \verb!time!,
that registered timing with a precision of hundredths of a second. Nonetheless,
this didn't influence the test too much. To reduce possible outliers we performed
the test $100$ times. With this $N$, the total time spent by the Virtual
Machines to boot up was of $2021,15$ seconds, while with containers the same
number of start ups resulted in a total of $1.638$ seconds. Summing up, Docker
employs only the $0,08\%$ of the overall time spent for the test, underlining
how isolating the process with a set of defined policy and avoiding a
virtualized kernel boot-up saves a considerable amount of time.

@@

% TODO is it worth to keep it as a long table?
\begin{longtable}[c]{c|c|c}
\textbf{SFC length} & \textbf{Stamdard deviation (seconds)} & \textbf{Average 
deploy time (seconds)} \\ \hline
\endhead
%
\textbf{1}          & 2.560102                   & 13,291                     \\
\textbf{2}          & 0.6301444                  & 14,207                     \\
\textbf{3}          & 1.14903                    & 15,345                     \\
\textbf{4}          & 3.592179                   & 16,453                     \\
\textbf{5}          & 0.9728132                  & 16,634                     \\
\textbf{6}          & 1.103802                   & 17,418                     \\
\textbf{7}          & 1.561451                   & 18,815                     \\
\textbf{8}          & 0.7698537                  & 20,856                     \\
\textbf{9}          & 1.889197                   & 20,187                     \\
\textbf{10}         & 1.709227                   & 20,476                     \\
\caption[SFC start up time]{Table of the results. It is possible to see how the
  time required for the SFC to go up increases with the length, reaching an
  average of 20 seconds for chain of eight, nine and ten elements.}
\label{chap:tests:sec:sfclength:tab:sfcdata}\\
\end{longtable}

>>>>

It is worth saying that Docker metrics are generally more precise than the
Virtual Box one: Docker allows to inspect the container and to gain startup and
shutdown times with a precision of milliseconds, while to gather this
information for VirtualBox instances we had to use the command line utility
\verb!time!, that registered timing with a precision of hundredths of a second.
Nonetheless,this didn't influence the test too much. To reduce possible
outliers we performed
the test $100$ times. With this $N$, the total time spent by the Virtual
Machines to boot up was of $2021,15$ seconds, while with containers the same
number of start ups resulted in a total of $1.638$ seconds. Summing up, Docker
employs only the $0,08\%$ of the overall time spent for the test, underlining
how isolating the process with a set of defined policy and avoiding a
virtualized kernel boot-up saves a considerable amount of time.

@@

% TODO is it worth to keep it as a long table?
\begin{longtable}[c]{c|c|c}
\textbf{SFC length} & \textbf{Standard deviation (seconds)} & \textbf{Average 
deploy time (seconds)} \\ \hline
\endhead
%
\textbf{1}          & 2.560102                   & 13,291                     \\
\textbf{2}          & 0.6301444                  & 14,207                     \\
\textbf{3}          & 1.14903                    & 15,345                     \\
\textbf{4}          & 3.592179                   & 16,453                     \\
\textbf{5}          & 0.9728132                  & 16,634                     \\
\textbf{6}          & 1.103802                   & 17,418                     \\
\textbf{7}          & 1.561451                   & 18,815                     \\
\textbf{8}          & 0.7698537                  & 20,856                     \\
\textbf{9}          & 1.889197                   & 20,187                     \\
\textbf{10}         & 1.709227                   & 20,476                     \\
\caption[SFC start up time]{Table of the results. It is possible to see how the
  time required for the SFC to go up increases with the length, reaching an
  average of 20 seconds for chain of eight, nine and ten elements.}
\label{chap:tests:sec:sfclength:tab:sfcdata}\\
\end{longtable}
